---
title: "R Notebook"
output: html_notebook
---

Lets get the libraries set up
````{r}
#install.packages("tmap")
#library(tmap)


````



Connect to the DB
````{r}
# install.packages("RPostgreSQL")
require("RPostgreSQL")
# create a connection
# save the password that we can "hide" it as best as we can by collapsing it
pw <- {"ruser"}



# loads the PostgreSQL driver

drv <- dbDriver("PostgreSQL")
# creates a connection to the postgres database
# note that "con" will be used later in each connection to the database
con <- dbConnect(drv, dbname = "cali_water",
                 host = "localhost", port = 5432,
                 user = "ruser", password = pw)

````



Let's view the tables by showing all tables that are accessible by the current user:

````{r}
sqlquerry <- dbGetQuery(con, "SELECT * FROM information_schema.tables WHERE table_schema = 'public';")
#sqlquerry
table_names <- array(sqlquerry['table_name'])
#table_names

#table_names[1,1]
#table_names[2,1]
#table_names[3,1]
#table_names[4,1]

table_names_list <- c()
for (e in table_names[,1])
  {
    table_names_list <- append(table_names_list, e)
  }

table_names_list
````

Let's explor each of these tables. Finding unique items and ranges

````{r}
# stations <- data.frame(dbGetQuery(con, "SELECT * FROM stations"))
# station_sample <- stations[sample(1:nrow(stations), 10), ]
# station_sample
# 
lab_results <- data.frame(dbGetQuery(con, "SELECT * FROM lab_results"))
lab_results_sample <- lab_results[sample(1:nrow(lab_results), 10), ]
lab_results_sample
# 
# field_results <- data.frame(dbGetQuery(con, "SELECT * FROM field_results"))
# field_results_sample <- field_results[sample(1:nrow(field_results), 10), ]
# field_results_sample
# 
# period_of_record <- data.frame(dbGetQuery(con, "SELECT * FROM period_of_record"))
# period_of_record_sample <- period_of_record[sample(1:nrow(period_of_record), 10), ]
# period_of_record_sample
````



Unique counties: 
````{r}
unique_counties <- unique(lab_results['county_name'])
unique_counties
````


Let's look at Alameda
````{r}
Alameda <- data.frame(dbGetQuery(con, "SELECT * FROM stations WHERE county_name = 'Alameda'"))
Alameda_sample <- Alameda[sample(1:nrow(Alameda), 10), ]
Alameda_sample

unique(Alameda['station_name'])
````

Lab Results for Alameda
````{r}
Alameda_Lab_results <- data.frame(dbGetQuery(con, "SELECT * FROM lab_results WHERE (units = 'mg/L' AND county_name = 'Alameda' AND parameter LIKE '%Dissolved%')"))
Alameda_Lab_results_sample <- Alameda_Lab_results[sample(1:nrow(Alameda_Lab_results), 10), ]
Alameda_Lab_results_sample

unique(Alameda_Lab_results['station_name'])
unique(Alameda_Lab_results['station_id'])
unique(Alameda_Lab_results['units'])
unique(Alameda_Lab_results['parameter'])

length(subset(Alameda_Lab_results, Alameda_Lab_results['units'] == "mg/L"))
mgl <- subset(Alameda_Lab_results, Alameda_Lab_results$units == "mg/L")
mgl
````

Let's boxplot
````{r}
Alameda_Lab_results_sample
png("rplot_SAMPLE.png", width = 4096, height = 2000)
boxplot(Alameda_Lab_results_sample$result ~ Alameda_Lab_results_sample$parameter, las = 2)
dev.off()

````

And now with the full set

````{r}
Fresno_Lab_results <- data.frame(dbGetQuery(con, "SELECT * FROM lab_results WHERE (units = 'mg/L' AND county_name = 'Fresno' AND parameter LIKE '%Dissolved%')"))

Fresno_Lab_results_subset <- subset(Fresno_Lab_results, Fresno_Lab_results$parameter == "Total Dissolved Solids")
#Fresno_Lab_results_subset <- subset(Fresno_Lab_results, Fresno_Lab_results$units == "mg/L")
boxplot(Fresno_Lab_results_subset$result ~ Fresno_Lab_results_subset$parameter, ylim = c(0,500))

png("frezno_lab_results.png", width = 4096, height = 4096)
par(mar = c(25, 5, 5, 5))
boxplot(Fresno_Lab_results$result ~ Fresno_Lab_results$parameter, las = 2, ylim = c(0, 8500))
dev.off()

png("frezno_lab_results_log.png", width = 4096, height = 4096)
par(mar = c(25, 5, 5, 5))
boxplot(log(Fresno_Lab_results$result) ~ Fresno_Lab_results$parameter, las = 2, ylim = c(0, 4500))
dev.off()
````
What about time?

````{r}

range(Alameda_Lab_results$sample_date)


````



Let's make a for loop to create a string for the db sql requests


````{r}
lab_results <- data.frame(dbGetQuery(con, "SELECT * FROM lab_results"))
unique_counties <- unique(lab_results['county_name'])
````


````{r}
for (i in unique_counties$county_name)
  {
    sql_string <- paste("SELECT * FROM lab_results WHERE (units = 'mg/L' AND county_name = '", i, "' AND parameter LIKE '%Dissolved%')", sep="")
    Alameda_Lab_results <- data.frame(dbGetQuery(con, sql_string))

    png(paste(i,"_","lab_results.png", sep = ""), width = 4096, height = 1000)
    par(mar = c(25, 5, 5, 5))
    boxplot(Alameda_Lab_results$result ~ Alameda_Lab_results$parameter, las = 2, ylim = c(0, 2000))
    dev.off()
    
    # png(paste(i,"_","lab_results_log.png", sep = ""), width = 4096, height = 1000)
    # par(mar = c(25, 5, 5, 5))
    # boxplot(log(Alameda_Lab_results$result) ~ Alameda_Lab_results$parameter, las = 2, ylim = c(0, 2000))
    # dev.off()
    
    rm(sql_string)
    rm(Alameda_Lab_results)
  }

````





Let's look at time series, again
````{r}

sql_string <- paste("SELECT * FROM lab_results WHERE (units = 'mg/L' AND county_name = 'Alameda' AND parameter LIKE '%Dissolved%')", sep="")
Alameda_Lab_results <- data.frame(dbGetQuery(con, sql_string))

test_date <- as.Date(Alameda_Lab_results$sample_date[9])
print(as.Date(Alameda_Lab_results$sample_date[9])) 
print(as.Date(Alameda_Lab_results$sample_date[7])) 
print(as.Date(Alameda_Lab_results$sample_date[3])) 

typeof(Alameda_Lab_results$sample_date)
class(Alameda_Lab_results$sample_date)
attributes(Alameda_Lab_results$sample_date)

somedate <- as.Date(Alameda_Lab_results$sample_date[9], format = "%y-%m-%d")
format(somedate, format="%Y")

# Alameda_Lab_results$sample_date[format(somedate, format="%Y") >= 1970 && format(somedate, format="%Y") <= 1979]
# theseventies <- Alameda_Lab_results$sample_date[format(Alameda_Lab_results$sample_date, format="%Y") == range(1970:1979)]
# theseventies <- subset(Alameda_Lab_results, format(Alameda_Lab_results$sample_date, format="%Y") = range(1970:1979))
# whatsthis<-Alameda_Lab_results$sample_date[range(1970:1979)]
# subset(Alameda_Lab_results, )
# theseventies <- Alameda_Lab_results[subset(Alameda_Lab_results, Alameda_Lab_results$sample_date[as.character(format(Alameda_Lab_results$sample_date, format = "%Y") == "1971")]
# theseventies <- data.frame(subset(Alameda_Lab_results, Alameda_Lab_results$sample_date[as.character(format(Alameda_Lab_results$sample_date, format = "%Y"))] == 1971))
# theseventies <- subset(Alameda_Lab_results$sample_date, Alameda_Lab_results$sample_date[format(Alameda_Lab_results$sample_date, format = "%Y")] == 1971)



####WORKS####
#theseventies <- subset(Alameda_Lab_results, format(Alameda_Lab_results$sample_date, format = "%Y") == 1970)
#############



startstopyears <- range(format(Alameda_Lab_results$sample_date, format = "%Y"))
totalrange <- (startstopyears[1]:startstopyears[2])
workingset <- data.frame(subset(Alameda_Lab_results, format(Alameda_Lab_results$sample_date, format = "%Y") == 1983))

#for (i in seq(startstopyears[1]:startstopyears[2]))
for (i in totalrange)  
  {
    workingset <- data.frame(subset(Alameda_Lab_results, format(Alameda_Lab_results$sample_date, format = "%Y") == 1983))
    print(paste("Working on: ", i))
    rm(workingset)
  }

````


Getting a bit cluttered, let's start anew.
````{r}
# install.packages("RPostgreSQL")
require("RPostgreSQL")
# create a connection
# save the password that we can "hide" it as best as we can by collapsing it
pw <- {"ruser"}



# loads the PostgreSQL driver

drv <- dbDriver("PostgreSQL")
# creates a connection to the postgres database
# note that "con" will be used later in each connection to the database
con <- dbConnect(drv, dbname = "cali_water",
                 host = "localhost", port = 5432,
                 user = "ruser", password = pw)

sql_string <- paste("SELECT * FROM lab_results WHERE (units = 'mg/L' AND county_name = 'Alameda' AND parameter LIKE '%Dissolved%')", sep="")
Alameda_Lab_results <- data.frame(dbGetQuery(con, sql_string))
startstopyears <- range(format(Alameda_Lab_results$sample_date, format = "%Y"))
totalrange <- (startstopyears[1]:startstopyears[2])
workingset <- data.frame(subset(Alameda_Lab_results, format(Alameda_Lab_results$sample_date, format = "%Y") == 1983))

````

